\newpage
\section{Summary}


This article includes the study on energy consumption on multiple levels; the first part of the work shows the importance of energy consumption in manufacturing industry. The research find that the big amount of energy consumed during manufacturing and the importance of energy savings. The study about the macroscopic view for the industry energy cost showed the importance of studying energy consumption and efficient improvement. 

The outline of the 
graph showed the energy consumption, literature review for energy consumption in manufacturing industry from machine to factory level. For machine level, a general method is shown for the calculation of energy consumption. An inventory of different machining processes are made and are based on the overall life cycle analysis. The possible improvement strategies are provided for a general process and for four specific processes. After that, the energy analyze for multi-machine system shows the energy connection of machines, together with the energy flows simulation. At last, review of factory level energy consumption is conducted, and investigate towards several directions in order to make factories more energy efficient for further discussion. 

Analysis of energy consumption is a major part in understanding a machine, factory. A combination of models, software and measurements is necessary to perform such an analysis. When done correctly, bottleneck machines can be discovered for manufacturing line levels or high energy consumption sub-process are brought to light in machine level. Energy improvement is done from the start of building or choosing machine/manufacturing line until the end when it is dismantled. Improvement strategies are similar over all the levels, e.g. energy management, new components or machines, etc.

An integrated effort over all the levels is necessary when we want to see a big improvement in energy consumption. Duflou et al. \cite{Duflou2012} predicts a 50\% improvement when global improvements are made in manufacturing

This study reviewed, a wide variety of considerations with relation to environmental impact reducing measures in general and energy and resource efficiency in specific has been discussed and the identified methods and techniques for analysis and system optimization.




